---
title: "AILA 2020 Task 1"
author: "Giorgio Maria Di Nunzio"
date: "2020/12/19"
output: html_document
---

# IMS - UNIPD @ AILA FIRE 2020

In this document, you will find the source code to reproduce the experiments of the paper *A Study on Lemma vs Stem for Legal Information Retrieval Using R Tidyverse* presented at the Track Artificial Intelligence for Legal Assistance at [http://fire.irsi.res.in/fire/2020/home](FIRE 2020). 


```{r setup, include=FALSE, echo=TRUE, eval=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Load libraries

These are the libraries needed for the experiments.

```{r libraries, echo=TRUE, eval=FALSE}

library(stringr)
library(dplyr)
library(tidytext)
library(textstem)
library(SnowballC)
library(readr)

```

## Load data 

You should read the dataset with the file "read_dataset.R" and then transform the text with "build_word_stem_lemma". You need to modify the code in order to point to your local path where the dataset is. 

```{r build, echo=TRUE, eval=FALSE}

# read dataset (need to the right path do the dataset)
source("src/read_dataset.R")
source("src/read_dataset_new_cases.R")

# original code
source("src/build_word_stem_lemma.R")

# update with new casedocs
source("src/build_word_stem_lemma_2020.R")

```


Alternatively, if the files have already been processed, you can reload them from the *imported* folder (that should be created in the first step).

```{r load, echo=TRUE, eval=FALSE}

files_to_read <- list.files("./imported/")

for (f in files_to_read) {

  assign(str_sub(f, end = -5), readRDS(file = paste0("./imported/", f)))

}

```

Remember that around September 20th, a new set of casedocs was released.

```{r load_2020, echo=TRUE, eval=FALSE}

files_to_read <- list.files("./imported_2020/")

for (f in files_to_read) {

  assign(str_sub(f, end = -5), readRDS(file = paste0("./imported/", f)))

}

```


## Train tf-idf

### Run with lemma

Build tfidf matrix (dataset and query) with lemmas

```{r tfidf_lemma, echo=TRUE, eval=FALSE}

source("src/build_run_lemma.R")

```

Now create run for training data

```{r run_train_lemma, echo=TRUE, eval=FALSE}

ranking_term_score_train_lemma <- queries_train_lemma_tf_idf_norm %>%
  rename(tf_idf_q = tf_idf) %>%
  inner_join(casedocs_lemma_tf_idf_norm) %>%
  mutate(term_score = (tf_idf_q * tf_idf) / (norm_q * norm_doc)) %>%
  select(query, lemma, doc_id, term_score) %>%
  group_by(query, doc_id) #%>% arrange(query, desc(term_score))

ranking_doc_score <- ranking_term_score_train_lemma %>%
  summarise(doc_score = sum(term_score))

run <- ranking_doc_score %>%
  group_by(query) %>%
  arrange(query, desc(doc_score), doc_id) %>%
  mutate(Q0 = "Q0", rank = row_number(), run_name = "ims_unipd_tfidf_lemma_casedocs") %>%
  select(query, Q0, doc_id, rank, doc_score, run_name) %>%
  top_n(n = 1000, wt = doc_score)
run
write_delim(run, path = "train/ims_unipd_tfidf_lemma_casedocs", col_names = FALSE, delim = " ")

ranking_term_score_train_lemma <- queries_train_lemma_tf_idf_norm %>%
  rename(tf_idf_q = tf_idf) %>%
  inner_join(statutes_lemma_tf_idf_norm) %>%
  mutate(term_score = (tf_idf_q * tf_idf) / (norm_q * norm_doc)) %>%
  select(query, lemma, doc_id, term_score) %>%
  group_by(query, doc_id) #%>% arrange(query, desc(term_score))

ranking_doc_score <- ranking_term_score_train_lemma %>%
  summarise(doc_score = sum(term_score))

run <- ranking_doc_score %>%
  group_by(query) %>%
  arrange(query, desc(doc_score), doc_id) %>%
  mutate(Q0 = "Q0", rank = row_number(), run_name = "ims_unipd_tfidf_lemma_statutes") %>%
  select(query, Q0, doc_id, rank, doc_score, run_name) %>%
  top_n(n = 1000, wt = doc_score)
run
write_delim(run, path = "train/ims_unipd_tfidf_lemma_statutes", col_names = FALSE, delim = " ")

```

Create run for test data

```{r run_test_lemma, echo=TRUE, eval=FALSE}

ranking_term_score_test_lemma <- queries_test_lemma_tf_idf_norm %>%
  rename(tf_idf_q = tf_idf) %>%
  inner_join(casedocs_lemma_tf_idf_norm) %>%
  mutate(term_score = (tf_idf_q * tf_idf) / (norm_q * norm_doc)) %>%
  select(query, lemma, doc_id, term_score) %>%
  group_by(query, doc_id) #%>% arrange(query, desc(term_score))

ranking_doc_score <- ranking_term_score_test_lemma %>%
  summarise(doc_score = sum(term_score))

run <- ranking_doc_score %>%
  group_by(query) %>%
  arrange(query, desc(doc_score), doc_id) %>%
  mutate(Q0 = "Q0", rank = row_number(), run_name = "ims_unipd_tfidf_lemma_casedocs") %>%
  select(query, Q0, doc_id, rank, doc_score, run_name) %>%
  top_n(n = 1000, wt = doc_score)
run
write_delim(run, path = "test/ims_unipd_tfidf_lemma_casedocs", col_names = FALSE, delim = " ")


ranking_term_score_test_lemma <- queries_test_lemma_tf_idf_norm %>%
  rename(tf_idf_q = tf_idf) %>%
  inner_join(statutes_lemma_tf_idf_norm) %>%
  mutate(term_score = (tf_idf_q * tf_idf) / (norm_q * norm_doc)) %>%
  select(query, lemma, doc_id, term_score) %>%
  group_by(query, doc_id) #%>% arrange(query, desc(term_score))

ranking_doc_score <- ranking_term_score_test_lemma %>%
  summarise(doc_score = sum(term_score))

run <- ranking_doc_score %>%
  group_by(query) %>%
  arrange(query, desc(doc_score), doc_id) %>%
  mutate(Q0 = "Q0", rank = row_number(), run_name = "ims_unipd_tfidf_lemma_statutes") %>%
  select(query, Q0, doc_id, rank, doc_score, run_name) %>%
  top_n(n = 1000, wt = doc_score)
run
write_delim(run, path = "test/ims_unipd_tfidf_lemma_statutes", col_names = FALSE, delim = " ")

```

Re-run on new casedocs dataset.

```{r run_test_lemma_2020, echo=TRUE, eval=FALSE}

ranking_term_score_test_lemma <- queries_test_lemma_tf_idf_norm %>%
  rename(tf_idf_q = tf_idf) %>%
  inner_join(casedocs_lemma_tf_idf_norm) %>%
  mutate(term_score = (tf_idf_q * tf_idf) / (norm_q * norm_doc)) %>%
  select(query, lemma, doc_id, term_score) %>%
  group_by(query, doc_id) #%>% arrange(query, desc(term_score))

ranking_doc_score <- ranking_term_score_test_lemma %>%
  summarise(doc_score = sum(term_score))

run <- ranking_doc_score %>%
  group_by(query) %>%
  arrange(query, desc(doc_score), doc_id) %>%
  mutate(Q0 = "Q0", rank = row_number(), run_name = "ims_unipd_tfidf_lemma_casedocs") %>%
  select(query, Q0, doc_id, rank, doc_score, run_name) %>%
  top_n(n = 1000, wt = doc_score)
run
write_delim(run, path = "test_2020/ims_unipd_tfidf_lemma_casedocs", col_names = FALSE, delim = " ")


```


<!-- Quick evaluation -->

<!-- ```{r} -->

<!-- qrels_num_rel <- qrels_casedocs_train %>% -->
<!--   group_by(query) %>% -->
<!--   summarise(num_rel = sum(relevance)) -->

<!-- run_with_rel <- run %>% -->
<!--   rename(doc = doc_id) %>% -->
<!--   inner_join(qrels_casedocs_train) -->

<!-- P_10 <- run_with_rel %>% -->
<!--   group_by(query) %>% -->
<!--   top_n(10, wt = doc_score) %>% -->
<!--   summarize(rel_ret = sum(relevance)) %>% -->
<!--   inner_join(qrels_num_rel) %>% -->
<!--   mutate(P_10 = rel_ret / 10) -->

<!-- mean(P_10$P_10) -->


<!-- ``` -->


### Run with stem

Build tfidf matrix (dataset and query) with lemmas

```{r tfidf_stem, echo=TRUE, eval=FALSE}

source("build_run_stem.R")

```

Build run

```{r run_train_stem, echo=TRUE, eval=FALSE}

ranking_term_score_train_stem <- queries_train_stem_tf_idf_norm %>%
  rename(tf_idf_q = tf_idf) %>%
  inner_join(casedocs_stem_tf_idf_norm) %>%
  mutate(term_score = (tf_idf_q * tf_idf) / (norm_q * norm_doc)) %>%
  select(query, stem, doc_id, term_score) %>%
  group_by(query, doc_id) #%>% arrange(query, desc(term_score))

ranking_doc_score <- ranking_term_score_train_stem %>%
  summarise(doc_score = sum(term_score))

run <- ranking_doc_score %>%
  group_by(query) %>%
  arrange(query, desc(doc_score), doc_id) %>%
  mutate(Q0 = "Q0", rank = row_number(), run_name = "ims_unipd_tfidf_stem_casedocs") %>%
  select(query, Q0, doc_id, rank, doc_score, run_name) %>%
  top_n(n = 1000, wt = doc_score)
run
write_delim(run, path = "train/ims_unipd_tfidf_stem_casedocs", col_names = FALSE, delim = " ")

ranking_term_score_train_stem <- queries_train_stem_tf_idf_norm %>%
  rename(tf_idf_q = tf_idf) %>%
  inner_join(statutes_stem_tf_idf_norm) %>%
  mutate(term_score = (tf_idf_q * tf_idf) / (norm_q * norm_doc)) %>%
  select(query, stem, doc_id, term_score) %>%
  group_by(query, doc_id) #%>% arrange(query, desc(term_score))

ranking_doc_score <- ranking_term_score_train_stem %>%
  summarise(doc_score = sum(term_score))

run <- ranking_doc_score %>%
  group_by(query) %>%
  arrange(query, desc(doc_score), doc_id) %>%
  mutate(Q0 = "Q0", rank = row_number(), run_name = "ims_unipd_tfidf_stem_statutes") %>%
  select(query, Q0, doc_id, rank, doc_score, run_name) %>%
  top_n(n = 1000, wt = doc_score)
run
write_delim(run, path = "train/ims_unipd_tfidf_stem_statutes", col_names = FALSE, delim = " ")


```

Build test run

```{r run_test_stem, echo=TRUE, eval=FALSE}

ranking_term_score_test_stem <- queries_test_stem_tf_idf_norm %>%
  rename(tf_idf_q = tf_idf) %>%
  inner_join(casedocs_stem_tf_idf_norm) %>%
  mutate(term_score = (tf_idf_q * tf_idf) / (norm_q * norm_doc)) %>%
  select(query, stem, doc_id, term_score) %>%
  group_by(query, doc_id) #%>% arrange(query, desc(term_score))

ranking_doc_score <- ranking_term_score_test_stem %>%
  summarise(doc_score = sum(term_score))

run <- ranking_doc_score %>%
  group_by(query) %>%
  arrange(query, desc(doc_score), doc_id) %>%
  mutate(Q0 = "Q0", rank = row_number(), run_name = "ims_unipd_tfidf_stem_casedocs") %>%
  select(query, Q0, doc_id, rank, doc_score, run_name) %>%
  top_n(n = 1000, wt = doc_score)
run
write_delim(run, path = "test/ims_unipd_tfidf_stem_casedocs", col_names = FALSE, delim = " ")

ranking_term_score_test_stem <- queries_test_stem_tf_idf_norm %>%
  rename(tf_idf_q = tf_idf) %>%
  inner_join(statutes_stem_tf_idf_norm) %>%
  mutate(term_score = (tf_idf_q * tf_idf) / (norm_q * norm_doc)) %>%
  select(query, stem, doc_id, term_score) %>%
  group_by(query, doc_id) #%>% arrange(query, desc(term_score))

ranking_doc_score <- ranking_term_score_test_stem %>%
  summarise(doc_score = sum(term_score))

run <- ranking_doc_score %>%
  group_by(query) %>%
  arrange(query, desc(doc_score), doc_id) %>%
  mutate(Q0 = "Q0", rank = row_number(), run_name = "ims_unipd_tfidf_stem_statutes") %>%
  select(query, Q0, doc_id, rank, doc_score, run_name) %>%
  top_n(n = 1000, wt = doc_score)
run
write_delim(run, path = "test/ims_unipd_tfidf_stem_statutes", col_names = FALSE, delim = " ")

```


```{r run_test_stem_2020, echo=TRUE, eval=FALSE}

ranking_term_score_test_stem <- queries_test_stem_tf_idf_norm %>%
  rename(tf_idf_q = tf_idf) %>%
  inner_join(casedocs_stem_tf_idf_norm) %>%
  mutate(term_score = (tf_idf_q * tf_idf) / (norm_q * norm_doc)) %>%
  select(query, stem, doc_id, term_score) %>%
  group_by(query, doc_id) #%>% arrange(query, desc(term_score))

ranking_doc_score <- ranking_term_score_test_stem %>%
  summarise(doc_score = sum(term_score))

run <- ranking_doc_score %>%
  group_by(query) %>%
  arrange(query, desc(doc_score), doc_id) %>%
  mutate(Q0 = "Q0", rank = row_number(), run_name = "ims_unipd_tfidf_stem_casedocs") %>%
  select(query, Q0, doc_id, rank, doc_score, run_name) %>%
  top_n(n = 1000, wt = doc_score)
run
write_delim(run, path = "test_2020/ims_unipd_tfidf_stem_casedocs", col_names = FALSE, delim = " ")

```


<!-- Quick evaluation -->

<!-- ```{r} -->

<!-- qrels_num_rel <- qrels_casedocs_train %>% -->
<!--   group_by(query) %>% -->
<!--   summarise(num_rel = sum(relevance))  -->

<!-- run_with_rel <- run %>% -->
<!--   rename(doc = doc_id) %>% -->
<!--   inner_join(qrels_casedocs_train)  -->

<!-- P_10 <- run_with_rel %>% -->
<!--   group_by(query) %>% -->
<!--   #filter(rank < 11) %>% -->
<!--   top_n(10, wt = doc_score) %>% -->
<!--   summarize(rel_ret = sum(relevance)) %>% -->
<!--   inner_join(qrels_num_rel) %>% -->
<!--   mutate(P_10 = rel_ret / 10) -->

<!-- mean(P_10$P_10) -->


<!-- ``` -->


<!-- ### Run with word -->

<!-- Build tfidf matrix (dataset and query) with word (not used in AILA2020) -->

<!-- ```{r tfidf_stem} -->

<!-- source("build_run_word.R") -->

<!-- ``` -->

<!-- Build run -->

<!-- ```{r run_train_word} -->

<!-- ranking_term_score_train_word <- queries_train_word_tf_idf_norm %>% -->
<!--   rename(tf_idf_q = tf_idf) %>% -->
<!--   inner_join(casedocs_word_tf_idf_norm) %>% -->
<!--   mutate(term_score = (tf_idf_q * tf_idf) / (norm_q * norm_doc)) %>% -->
<!--   select(query, word, doc_id, term_score) %>% -->
<!--   group_by(query, doc_id) #%>% arrange(query, desc(term_score)) -->

<!-- ranking_doc_score <- ranking_term_score_train_word %>% -->
<!--   summarise(doc_score = sum(term_score)) -->

<!-- run <- ranking_doc_score %>% -->
<!--   group_by(query) %>% -->
<!--   arrange(query, desc(doc_score), doc_id) %>% -->
<!--   mutate(Q0 = "Q0", rank = row_number(), run_name = "tfidf_word") %>% -->
<!--   select(query, Q0, doc_id, rank, doc_score, run_name) %>% -->
<!--   top_n(n = 1000, wt = doc_score) -->
<!-- run   -->
<!-- write_delim(run, path = "runs/tfidf_word.txt", col_names = FALSE, delim = " ") -->

<!-- ``` -->

## Train BM25

### Run with lemma

Build bm25 matrix (dataset and query) with lemmas

```{r bm25_lemma, echo=TRUE, eval=FALSE}

source("src/bm25_lemma.R")

```

Now create run for training data

```{r run_train_bm25, echo=TRUE, eval=FALSE}

ranking_term_score_train_lemma <- queries_train_lemma_tf_idf %>%
  rename(tf_idf_q = tf_idf) %>%
  inner_join(select(casedocs_lemma_bm25, doc_id, lemma, bm25_score)) %>%
  select(query, lemma, doc_id, bm25_score) %>%
  group_by(query, doc_id) #%>% arrange(query, desc(term_score))

ranking_doc_score <- ranking_term_score_train_lemma %>%
  summarise(doc_score = sum(bm25_score))

run <- ranking_doc_score %>%
  group_by(query) %>%
  arrange(query, desc(doc_score), doc_id) %>%
  mutate(Q0 = "Q0", rank = row_number(), run_name = "ims_unipd_bm25_lemma_casedocs") %>%
  select(query, Q0, doc_id, rank, doc_score, run_name) %>%
  top_n(n = 1000, wt = doc_score)
run
write_delim(run, path = "train/ims_unipd_bm25_lemma_casedocs", col_names = FALSE, delim = " ")


ranking_term_score_train_lemma <- queries_train_lemma_tf_idf %>%
  rename(tf_idf_q = tf_idf) %>%
  inner_join(select(statutes_lemma_bm25, doc_id, lemma, bm25_score)) %>%
  select(query, lemma, doc_id, bm25_score) %>%
  group_by(query, doc_id) #%>% arrange(query, desc(term_score))

ranking_doc_score <- ranking_term_score_train_lemma %>%
  summarise(doc_score = sum(bm25_score))

run <- ranking_doc_score %>%
  group_by(query) %>%
  arrange(query, desc(doc_score), doc_id) %>%
  mutate(Q0 = "Q0", rank = row_number(), run_name = "ims_unipd_bm25_lemma_statutes") %>%
  select(query, Q0, doc_id, rank, doc_score, run_name) %>%
  top_n(n = 1000, wt = doc_score)
run
write_delim(run, path = "train/ims_unipd_bm25_lemma_statutes", col_names = FALSE, delim = " ")


```


```{r run_test_bm25, echo=TRUE, eval=FALSE}

ranking_term_score_test_lemma <- queries_test_lemma_tf_idf %>%
  rename(tf_idf_q = tf_idf) %>%
  inner_join(select(casedocs_lemma_bm25, doc_id, lemma, bm25_score)) %>%
  select(query, lemma, doc_id, bm25_score) %>%
  group_by(query, doc_id) #%>% arrange(query, desc(term_score))

ranking_doc_score <- ranking_term_score_test_lemma %>%
  summarise(doc_score = sum(bm25_score))

run <- ranking_doc_score %>%
  group_by(query) %>%
  arrange(query, desc(doc_score), doc_id) %>%
  mutate(Q0 = "Q0", rank = row_number(), run_name = "ims_unipd_bm25_lemma_casedocs") %>%
  select(query, Q0, doc_id, rank, doc_score, run_name) %>%
  top_n(n = 1000, wt = doc_score)
run
write_delim(run, path = "test/ims_unipd_bm25_lemma_casedocs", col_names = FALSE, delim = " ")


ranking_term_score_test_lemma <- queries_test_lemma_tf_idf %>%
  rename(tf_idf_q = tf_idf) %>%
  inner_join(select(statutes_lemma_bm25, doc_id, lemma, bm25_score)) %>%
  select(query, lemma, doc_id, bm25_score) %>%
  group_by(query, doc_id) #%>% arrange(query, desc(term_score))

ranking_doc_score <- ranking_term_score_test_lemma %>%
  summarise(doc_score = sum(bm25_score))

run <- ranking_doc_score %>%
  group_by(query) %>%
  arrange(query, desc(doc_score), doc_id) %>%
  mutate(Q0 = "Q0", rank = row_number(), run_name = "ims_unipd_bm25_lemma_statutes") %>%
  select(query, Q0, doc_id, rank, doc_score, run_name) %>%
  top_n(n = 1000, wt = doc_score)
run
write_delim(run, path = "test/ims_unipd_bm25_lemma_statutes", col_names = FALSE, delim = " ")


```



```{r run_test_bm25_2020, echo=TRUE, eval=FALSE}

ranking_term_score_test_lemma <- queries_test_lemma_tf_idf %>%
  rename(tf_idf_q = tf_idf) %>%
  inner_join(select(casedocs_lemma_bm25, doc_id, lemma, bm25_score)) %>%
  select(query, lemma, doc_id, bm25_score) %>%
  group_by(query, doc_id) #%>% arrange(query, desc(term_score))

ranking_doc_score <- ranking_term_score_test_lemma %>%
  summarise(doc_score = sum(bm25_score))

run <- ranking_doc_score %>%
  group_by(query) %>%
  arrange(query, desc(doc_score), doc_id) %>%
  mutate(Q0 = "Q0", rank = row_number(), run_name = "ims_unipd_bm25_lemma_casedocs") %>%
  select(query, Q0, doc_id, rank, doc_score, run_name) %>%
  top_n(n = 1000, wt = doc_score)
run
write_delim(run, path = "test_2020/ims_unipd_bm25_lemma_casedocs", col_names = FALSE, delim = " ")


```
